Benchmarking of Rigetti architecture

### 2022-05-16 txt/rigetti.tex
v0 and v1 analitical form

\subsection{Construction of $V_0$ and $V_1$}
	It turned out that for case $\phi = \frac{k \pi}{16}$, where $k=0,\ldots,31$ the controlled unitary $V_0$ and $V_1$ have the following form
	\begin{equation}
	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi(16-k)}{64} \right)&-i \cos\left( \frac{\pi(16-k)}{64} \right)\\ \cos\left( \frac{\pi(16-k)}{64} \right)& \sin\left( \frac{\pi(16-k)}{64} \right)\end{array}\right) 
	\end{equation}

		\begin{equation}
	V_1 = \left(\begin{array}{cc}-i \cos\left( \frac{\pi(16-k)}{64} \right) &i \sin\left( \frac{\pi(16-k)}{64} \right)\\\sin\left( \frac{\pi(16-k)}{64} \right) &  \cos\left( \frac{\pi(16-k)}{64} \right) \end{array}\right) 
	\end{equation}

@@

	\caption{ A schematic representation of the setup for distinguishing
		measurements using postselection. 
	}\label{fig:postsellection}
\end{figure}
\begin{enumerate}
\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
\rangle. $
\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
\item We implement unitary $V_0 $ or $ V_1$.
\item We prepare the measurement $\Delta$ in standard basis (already exist on 
Rigetti architecture) on each qubits.
\item We calculate the probability of correct discrimination in the following 
way
\begin{equation}
p = ...
\end{equation}
\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
\end{enumerate}
\end{scheme}

>>>>

\subsection{Construction of $V_0$ and $V_1$}
	For each $\phi \in \R$,  the controlled unitary $V_0$ and $V_1$ have the following form
	\begin{equation}
	V_0 = \left(\begin{array}{cc}i \sin\left( \frac{\pi - \phi}{4} \right)&-i \cos\left( \frac{\pi - \phi}{4} \right)\\ \cos\left( \frac{\pi - \phi}{4}\right)& \sin\left( \frac{\pi - \phi}{4} \right)\end{array}\right),
	\end{equation}

		\begin{equation}
	V_1 = \left(\begin{array}{cc}-i \cos\left(\frac{\pi - \phi}{4}\right) &i \sin\left( \frac{\pi - \phi}{4}\right)\\\sin\left( \frac{\pi - \phi}{4} \right) &  \cos\left( \frac{\pi - \phi}{4} \right) \end{array}\right).
	\end{equation}

@@

	\caption{ A schematic representation of the setup for distinguishing
		measurements using postselection. 
	}\label{fig:postsellection}
\end{figure}
\begin{enumerate}
\item We prepare input state $\ket{\psi} = \frac{1}{\sqrt{2} } | \Id_2 \rangle 
\rangle. $
\item We prepare one of two unitary channel $\Phi_{U} $ or $\Phi_{\1}$. 
\item We implement unitary $V_0 $ or $ V_1$.
\item We prepare the measurement $\Delta$ in standard basis (already exists on 
Rigetti architecture) on each qubits.
\item We calculate the probability of correct discrimination in the following 
way
\begin{equation}
p = ...
\end{equation}
\todo[inline]{grubsza kmina, musze Ci to na zywo opowiedziec xd}
\end{enumerate}
\end{scheme}
